% SPDX-FileCopyrightText: Copyright (C) Nile Jocson <novoseiversia@gmail.com>
% SPDX-License-Identifier: MPL-2.0

\documentclass{article}

\input{../../common/cjmath.tex}



\begin{document}
	\cjboilerplate{Math 20}{Lines and Circles}

	\begin{cjsection}{}
		\cjitem{Find the value of \(k\) such that the lines with equations \(3x + 2y - 4 = 0\) and
		\(kx - 3y + 8\) are:}
			\cjsubitem{Parallel.}
				\begin{cjsolution}
					\cjwhy{\(2y = -3x + 4\)}{Rewrite the first equation in slope-intercept form.}
					\cjcontinue{\(y = -\frac{3}{2}x + 4\)}
					\cjwhy{\(-3y = -kx - 8\)}{Rewrite the second equation in slope-intercept form.}
					\cjcontinue{\(3y = kx + 8\)}
					\cjcontinue{\(y = \frac{k}{3}x + \frac{8}{3}\)}
					\cjwhy{\(\frac{k}{3} = -\frac{3}{2}\)}{Parallel slopes are equal.}
					\cjfa{\(k = -\frac{9}{2}\)}
				\end{cjsolution}

			\cjsubitem{Perpendicular.}
				\begin{cjsolution}
					\cjwhy{\(\frac{k}{3} = -\frac{1}{-\frac{3}{2}}\)}{Perpendicular slopes are the negative reciprocal of each other.}
					\cjcontinue{\(\frac{k}{3} = \frac{2}{3}\)}
					\cjfa{\(k = 2\)}
				\end{cjsolution}

		\cjitem{Line \(l\) is perpendicular to the line segment with endpoints \(P(-4, 7)\) and \(Q(2, -3)\).
		If \(l\) passes through the midpoint of the line segment \(\overline{PQ}\), find an equation for \(l\)
		in slope-intercept form.}
			\begin{cjsolution}
				\cjwhy{\(m = \frac{-3 - 7}{2 + 4}\)}{Find the slope of \(\overline{PQ}\).}
				\cjcontinue{\(m = \frac{-10}{6}\)}
				\cjcontinue{\(m = -\frac{5}{3}\)}
				\cjwhy{\(M = (\frac{-4 + 2}{2}, \frac{7 - 3}{2})\)}{Find the midpoint of \(\overline{PQ}\).}
				\cjcontinue{\(M = (\frac{-2}{2}, \frac{4}{2})\)}
				\cjcontinue{\(M = (-1, 2)\)}
				\cjwhy{\(y - 2 = -\frac{5}{3}(x + 1)\)}{Use the point-slope formula.}
				\cjcontinue{\(y - 2 = -\frac{5}{3}x - \frac{5}{3}\)}
				\cjcontinue{\(y = -\frac{5}{3}x - \frac{5}{3} + 2\)}
				\cjcontinue{\(y = -\frac{5}{3}x - \frac{5}{3} + \frac{6}{3}\)}
				\cjfa{\(y = -\frac{5}{3}x - \frac{1}{3}\)}
			\end{cjsolution}

		\cjitem{Find a general equation of the line that is parallel to the line with equation \(3x - y + 1 = 0\)
		and whose x-intercept is also the x-intercept of the line with equation \(2x - 3y + 6 = 0\)}
			\begin{cjsolution}
				\cjwhy{\(-y = -3x - 1\)}{Find the slope of the first equation.}
				\cjcontinue{\(y = 3x + 1\)}
				\cjcontinue{\(m = 3\)}
				\cjwhy{\(2x - 3(0) + 6 = 0\)}{Find the x-intercept of the second equation.}
				\cjcontinue{\(2x + 6 = 0\)}
				\cjcontinue{\(2x = -6\)}
				\cjcontinue{\(x = -3\)}
				\cjwhy{\(y = 3(x + 3)\)}{Use the point-slope formula.}
				\cjfa{\(y = 3x + 9\)}
			\end{cjsolution}
	\end{cjsection}
\end{document}
